Understanding the Data Duplication in VM Cloud Storage

### 2012-03-18 data_analysis/abs.tex
update

\begin{abstract}
Backup in VM cloud is mainly done by storing snapshots of
VM images. Since VM images are huge and backup is frequent, 
the snapshot storage
in VM cloud must deduplicate snapshot data to save cloud resources.
Thus it is very important to exploit the duplication pattern of snapshot
backup data for designing better cloud storage systems.
In this paper we present the data duplication pattern that
we observed from Aliyun's publie VM cloud services, and provide
some insights for researchers and engineers to design future
 deduplication strategies for VM cloud backup.
\end{abstract}

>>>>

\begin{abstract}
Backup in VM cloud is mainly done by storing snapshots of
VM images. Since VM images are huge and backup is frequent, 
the snapshot storage
in VM cloud must reduce snapshot data to save cloud resources.
Thus it is very important to exploit the duplication pattern of snapshot
backup data for developing better cloud storage system.
In this paper we present the data duplication pattern that
we observed from Aliyun's publie VM cloud services, and provide
some insights for researchers and engineers to design future
 deduplication strategies for VM cloud backup.
\end{abstract}
